---
title: "p8130_hw2_rq2166"
author: "Ruoyuan Qian"
date: "2019/10/02"
output:   
  html_document:
    toc: true
    toc_float: true
---
# Problem 1

```{r set up,message=FALSE}
library(ggplot2)
library(plyr)
library(readxl)
library(dplyr)
library(arsenal)
#install.packages("ggpubr")
library(ggpubr)
```
## a)

probability that in NYC exactly 30 cases occur
```{r }
lam = 5*8.5
n   = 30
dpois(n, lam)
```
## b)

Probability that in NYC exactly 30 cases in Asians occur
```{r}
lam_a = 0.14*0.39*8.5
n     = 30
dpois(n,lam_a)
```
The probability that in NYC exactly 30 cases in non-Hispanic Whites occur
```{r}
lam_w = 0.428*8.5*6.02
n     = 30
dpois(n,lam_w)
```
The probability that in NYC exactly 30 cases in Black occur
```{r }
#blacks
lam_b = 0.31*0.243*8.5
n     = 30
dpois(n,lam_b)
```
# Problem 2

Input data
```{r ,message=FALSE}

raw_data<-read_excel(".\\data\\Exercise.xlsx",skip =1)
 fixed_data    <-     raw_data %>% mutate(
         Group  =     recode(Group,  "0" = "Control","1" = "Intervention"),
         Gender =     recode(Gender, "1" = "male", "2" = "female"),
         HTN    =     recode(HTN,    "0" = "no",   "1" = "yes"),
         T2DM   =     recode(T2DM,   "0" = "no",   "1" = "yes"),
         Smokes =     recode(Smokes, "0" = "no",   "1" = "yes"),
         Depression = recode(Depression, "0" = "no", "1" = "yes"),
         Race   =     recode(Race,   "1" = "African American", 
                                     "2" = "Hispanic",
                                     "3" = "African American"))
#rename variables
 names(fixed_data)[c(9:20)]=c("SYS_PRE","SYS_POST","DIA_PRE","DIA_POST",
                              "BMI_PRE","BMI_POST","HDL_PRE","HDL_POST",
                              "LDL_PRE","LDL_POST","GLU_PRE","GLU_POST")
 
 

```
## a)
**As for the intervention group**

Paired-t.test using `t.test` function
```{r}
BMI_i = fixed_data %>% 
  filter(Group == "Intervention") %>% 
  select(BMI_POST,BMI_PRE )

t.test( BMI_i$BMI_POST, 
        BMI_i$BMI_PRE , 
        paired=T, alternative = "two.sided")
```
Paired-t.test calculating step by step using formulae
```{r }
d_i   = round(mean(BMI_i$BMI_POST - BMI_i$BMI_PRE),2)
sd_i  = round(sd((BMI_i$BMI_POST - BMI_i$BMI_PRE)),2)
n     = length(BMI_i$BMI_PRE)

# calculate the test-statistics
t_s = round(d_i/(sd_i/sqrt(n)),2)

# calculate t-value when type 1 error = .05
t_a = qt(0.975,n-1)

p_value = 2*round((pt(t_s,n-1)),5)
p_value

# calculate the confidence interval
CI = paste(round(d_i-round((qt(0.975,n-1)),2)*sqrt(sd_i^2/n),2),
           round(d_i+round((qt(0.975,n-1)),2)*sqrt(sd_i^2/n),2))
CI
```
**As for the control group**

Paired-t.test using `t.test` function
```{r}
BMI_c = fixed_data %>% 
  filter(Group == "Control") %>% 
  select(BMI_POST, BMI_PRE)

t.test(BMI_c$BMI_POST, BMI_c$BMI_PRE,paired=T)
```

Paired-t.test calculating step by step using formulae
```{r }
d_c   = round(mean(BMI_c$BMI_POST-BMI_c$BMI_PRE),2)
sd_c  = round(sd(BMI_c$BMI_POST-BMI_c$BMI_PRE),2)
n     = length(BMI_c$BMI_PRE)

# calculate the test-statistics
t_s = round(d_c/(sd_c/sqrt(n)),2)

# calculate t-value when type 1 error = .05
t_a = qt(0.975,n-1)

p_value = 2*(1-round((pt(t_s,n-1)),5))
p_value

# calculate the confidence interval
CI = paste(round(d_c-round((qt(0.975,n-1)),2)*sqrt(sd_c^2/n),2),
           round(d_c+round((qt(0.975,n-1)),2)*sqrt(sd_c^2/n),2))
CI
```
## b)
**Test the equality of the variance first**

F test using `var.test` function
```{r}
BMI_i = 
  BMI_i %>% 
  mutate(
    d_inter = BMI_POST - BMI_PRE)

BMI_c = 
  BMI_c %>% 
  mutate(
    d_con = BMI_POST - BMI_PRE)

var.test(BMI_i$d_inter,BMI_c$d_con, alternative = "two.sided")
```
F test calculating step by step using formulae
```{r }
# calculate the test-statistics
f_s = sd_i^2/sd_c^2

# calculate F-value when type 1 error = .05
f_a = qf(0.975,n-1,n-1)

f_s < f_a
```
Are the variances equal?``r f_s < f_a``
So the variance is not equal

Independent samples t-test for unequal variances using `t.test` function
```{r }
t.test(BMI_i$d_inter,BMI_c$d_con,
       paired=F,var.equal=FALSE,
       alternative = "two.sided")
```
Independent samples t-test for unequal variances calculating step by step using formulae
```{r }
# calculate the test-statistics
t_s = (d_i-d_c)/(sqrt(sd_i^2/n+sd_c^2/n))

# calculate the df value
df = ((sd_i^2/n) + (sd_c^2/n))^2/
     ((sd_i^2/n)^2/(n-1) + (sd_c^2/n)^2/(n-1))

# calculate t-value when type 1 error = .05
t_a = qt(0.975,round(df))


p_value = 2*round((pt(t_s,round(df))),5)
p_value

# calculate the confidence interval
CI = paste(round(d_i-d_c-round((qt(0.975,round(df))),2)*
                   sqrt(sd_i^2/n+sd_c^2/n),2),
           round(d_i-d_c+round((qt(0.975,round(df))),2)*
                   sqrt(sd_i^2/n+sd_c^2/n),2))
CI
```

## c)

### i) 
graph of density
```{r}
# grap for intervention group
fixed_data =fixed_data %>% 
  mutate(
    d=BMI_POST-BMI_PRE
  ) 

fixed_data %>% 
filter(Group=="Intervention") %>% 
 ggplot(aes(d,..density..))+
 geom_histogram(color = 'white',
                fill  = 'gray60',
                binwidth = .6)+
 geom_line(stat = 'density',size = 1)+
 expand_limits(x = c(-6,3)) +
    labs(
       title = "Density plot of intervention group",
       x     = "Difference in intervention group")


# grap for control group
fixed_data %>% 
filter(Group=="Control") %>% 
 ggplot(aes(d,..density..))+
 geom_histogram(color = 'white',
                fill  = 'gray60',
                binwidth = .6)+
 geom_line(stat = 'density',size = 1)+
  expand_limits(x = c(-4,4)) +
  labs(
     title = "Density plot of control group",
     x     = "Difference in control group")



```


graph for Q-Q plot
```{r}


ggqqplot(BMI_i$d_inter,main="Q-Q plot for intervention group")
ggqqplot(BMI_c$d_con,main="Q-Q plot for control group")

```


# Problem 3
## Exactly distribution
```{r}
n = 20
p = 0.6

# Probability that 10 or more restaurants
1-pbinom(9,n,p)
```
## Approximately distribution(Normality)
```{r}
mu = n*p
var = n*p*(1-p)

# probability that 10 or more restaurants(10<x<20)
round((pnorm(20.5,mu,sqrt(var))),5)-round((pnorm(9.5,mu ,sqrt(var))),5)

```
## Approximate distribution(Poisson)
```{r}
lambda = n*p

# probability that 10 or more restaurants
1 - ppois(9,lambda)
```

# Problem 4
## a)

Paired-t.test using `t.test` function
```{r}
with(sleep,
     t.test(extra[group == 2],
            extra[group == 1], paired = TRUE,
            alternative = "greater"))
```

Paired-t.test calculating step by step using formulae
```{r}
n  = with(sleep,length(extra[group == 2]))
d  = round(with(sleep,sum((extra[group == 2]-extra[group == 1]))/(n)),2)
sd = round(with(sleep,sd  (extra[group == 2]-extra[group == 1])),2)

# calculate the test-statistics
t_s = d/(sd/sqrt(n))

# calculate t-value when type 1 error = .05
t_a = qt(0.95,n-1)

p_value = 1-round((pt(t_s,n-1)),5)
p_value



```

## b)

```{r}
# calculate the confidence interval
CI = paste(round(d-round((qt(0.95,n-1)),2)*sqrt(sd^2/n),2),"Inf")
CI
```


## c) posteriori power

```{r}

delta = d

power=
  round(pt(-round((qt(1-0.05,n-1)),2) +
             delta/(sd/sqrt(n)),n-1),3)

power

```


