---
title: "p8130_hw2_rq2166"
author: "Ruoyuan Qian"
date: "2019/10/02"
output: word_document
---
# Problem 1

```{r}
library(ggplot2)
library(plyr)
```
## a)
```{r }
# probability that in NYC exactly 30 cases occurs
dpois(30, 42.5)
dbinom(30,8.5*1000000,5/1000000)
```
## b)
```{r }
#non-hispanic whites
lam_w = 0.428*8.5*6.02
dpois(30,lam_w)
n = 0.428*8.5*1000000
p = 6.02/1000000
dbinom(30,n,p)

#blacks
lam_b = 0.31*0.243*8.5
dpois(30,lam_b)
n = 0.243*8.5*1000000
p = 0.31/1000000
dbinom(30,n,p)

#Asian
lam_a = 0.14*0.39*8.5
dpois(30,lam_a)
n = 0.14*8.5*1000000
p = 0.39/1000000
dbinom(30,n,p)


```
According to the result, the probability of exactly 30 cases occur in non-hispanic whites is greater than the probability in NYC. However, as for other racial groups, the probability is extremely small and near to zero. 

# Problem 2

## input data
```{r ,message=FALSE}
library(readxl)
library(dplyr)
library(arsenal)
raw_data<-read_excel(".\\data\\Exercise.xlsx",skip =1)
 fixed_data    <-     raw_data %>% mutate(
         Group  =     recode(Group,  "0" = "Control","1" = "Intervention"),
         Gender =     recode(Gender, "1" = "male", "2" = "female"),
         HTN    =     recode(HTN,    "0" = "no",   "1" = "yes"),
         T2DM   =     recode(T2DM,   "0" = "no",   "1" = "yes"),
         Smokes =     recode(Smokes, "0" = "no",   "1" = "yes"),
         Depression = recode(Depression, "0" = "no", "1" = "yes"),
         Race   =     recode(Race,   "1" = "African American", 
                                     "2" = "Hispanic",
                                     "3" = "African American",
                                     "4" = "G"))
#rename variables
 names(fixed_data)[c(9:20)]=c("SYS_PRE","SYS_POST","DIA_PRE","DIA_POST",
                              "BMI_PRE","BMI_POST","HDL_PRE","HDL_POST",
                              "LDL_PRE","LDL_POST","GLU_PRE","GLU_POST")
 
 

```
## a)
```{r}
# post-pre
BMI_i = fixed_data %>% 
  filter(Group == "Intervention") %>% 
  select(BMI_POST,BMI_PRE )
BMI_i$BMI_PRE-BMI_i$BMI_POST
t.test(BMI_i$BMI_POST, BMI_i$BMI_PRE,paired=T,alternative = "two.sided")

d = BMI_i$BMI_PRE-BMI_i$BMI_POST
sqrt(sum((BMI_i$BMI_PRE-BMI_i$BMI_POST+0.76)^2)/35)
sqrt(sum((d-0.76)^2)/35)
sd(d)
length(BMI_i$BMI_PRE)
-0.76/(1.44/sqrt(36))
qt(0.975,35)
qnorm(0.975)
2*pt(-3.1742,35)
```

```{r}
BMI_c = fixed_data %>% 
  filter(Group == "Control") %>% 
  select(BMI_POST, BMI_PRE)
t.test(BMI_c$BMI_POST, BMI_c$BMI_PRE,paired=T)


d = BMI_c$BMI_POST-BMI_c$BMI_PRE
sqrt(sum((BMI_i$BMI_PRE-BMI_i$BMI_POST+0.76)^2)/35)
sqrt(sum((d-0.28)^2)/35)
sd(d)
length(BMI_i$BMI_PRE)
0.28/(0.97/sqrt(36))
qt(0.975,35)
qnorm(0.975)
0.28-2.03*0.97/6
2*(1-pt(1.7569,35))
```
## b)
```{r}

BMI_i = 
  BMI_i %>% 
  mutate(
    d_inter = BMI_POST - BMI_PRE
  )

BMI_c = 
  BMI_c %>% 
  mutate(
    d_con = BMI_POST - BMI_PRE
  )
qf(0.975,35,35)
var.test(BMI_i$d_inter,BMI_c$d_con, alternative = "two.sided")
## the variance is not equal
1.44^2/0.97^2
(-0.76-0.28)/(sqrt(1.44^2/36+0.97^2/36))
t.test(BMI_i$d_inter,BMI_c$d_con,paired=F,var.equal=FALSE,alternative = "two.sided")
dd=((1.44^2/36)+(0.97^2/36))^2/((1.44^2/36)^2/35+(0.97^2/36)^2/35)
pt(-3.61,61)
qt(0.975,61)
-0.76-0.28-qt(0.975,61)*sqrt((1.44^2/36)+(0.97^2/36))
```

## c)

### i) 

#### graph of normality
```{r}
fixed_data =fixed_data %>% 
  mutate(
    d=BMI_POST-BMI_PRE
  ) 


bmi_mean = ddply(fixed_data,"Group",summarise,
      bmi_pre_mean=mean(BMI_PRE),
      bmi_post_mean=mean(BMI_POST),
      bmi_d_mean=mean(d))

mu = fixed_data %>% 
       filter(Group =="Control") %>% 
       pull(d) %>% 
      mean()
var = fixed_data %>% 
       filter(Group =="Control") %>% 
       pull(d) %>% 
      var()

x<-rnorm(1000,mu,var)
funss<-function(x) 1/sqrt(2*pi*var)*exp(-(x-mu)^2/2*var^2)

 ggplot(fixed_data,aes( x = d, fill=Group)) +
  geom_density(alpha = .4) +
  expand_limits(x=c(-6,6)) +
  geom_vline(data=bmi_mean,
             aes(xintercept=bmi_d_mean,color=Group),
               linetype="dashed", size=1)+
  stat_function(fun = funss,geom="line",color="red",size=.2,alpha = .4)
 
 
mu = fixed_data %>% 
       filter(Group =="Intervention") %>% 
       pull(d) %>% 
      mean()
var = fixed_data %>% 
       filter(Group =="Intervention") %>% 
       pull(d) %>% 
      var()

x<-rnorm(1000,mu,var)
funss<-function(x) 1/sqrt(2*pi*var)*exp(-(x-mu)^2/2*var^2)

  fixed_data %>% 
    filter(Group=="Intervention") %>% 
 ggplot(aes( x = d, fill=Group)) +
  geom_density(alpha = .5) +
  expand_limits(x=c(-6,6)) +
  geom_vline(data=bmi_mean,
             aes(xintercept=bmi_d_mean[2]),
               linetype="dashed", size=0.5)+
  stat_function(fun = funss,geom="line",color="red",size=.7,alpha = .7)
  
  
  
mu = fixed_data %>% 
       filter(Group =="Control") %>% 
       pull(d) %>% 
      mean()
var = fixed_data %>% 
       filter(Group =="Control") %>% 
       pull(d) %>% 
      var()

x<-rnorm(1000,mu,var)
funss<-function(x) 1/sqrt(2*pi*var)*exp(-(x-mu)^2/2*var^2)

    fixed_data %>% 
    filter(Group=="Control") %>% 
 ggplot(aes( x = d, fill=Group)) +
  geom_density(alpha = .5,) +
  expand_limits(x=c(-6,6)) +
  geom_vline(data=bmi_mean,
             aes(xintercept=bmi_d_mean[1]),
               linetype="dashed", size=0.5)+
  stat_function(fun = funss,geom="line",color="red",size=.7,alpha = .7)

    
```

```{r}
install.packages('qqman')
library(qqman)

qqnorm(a) 
qqline(a)
  a %>% 
  fixed_data %>% 
 pull(d) %>% 
  
```


```{r}
x<-rnorm(1000,mu,var)
funss<-function(x) 1/sqrt(2*pi*var)*exp(-(x-mu)^2/2*var^2)

  fixed_data %>% 
    filter(Group=="Intervention") %>% 
 ggplot(aes(d,..density..))+
geom_histogram(color='white',fill='gray60',binwidth = .6)+
geom_line(stat='density',size=1)+
      expand_limits(x=c(-6,3)) +
    labs(
    title = "Density plot of intervention group",
    x = "Difference in intervention group")

  fixed_data %>% 
    filter(Group=="Control") %>% 
 ggplot(aes(d,..density..))+
geom_histogram(color='white',fill='gray60',binwidth = .6)+
geom_line(stat='density',size=1)+
  expand_limits(x=c(-4,4)) +
    labs(
    title = "Density plot of control group",
    x = "Difference in control group")



```

#### Normality test
```{r}
fixed_data %>% 
  filter(Group=="Intervention") %>% 
  pull(d) %>% 
shapiro.test()
  
  fixed_data %>% 
  filter(Group=="Control") %>% 
  pull(d) %>% 
shapiro.test()
```

According to the graphs, the distridution of Intervention is right skewed while the Control is approximately bell-shaped and can be seemed as normal distribution. 

# Problem 3
## exactly distribution
```{r}
1-pbinom(9,20,0.6)
```
## approximately distribution(normal)
```{r}
set.seed(1001)
n=20
p=0.6
x = dplyr::tibble(a =c(rbinom(10,n,p)) )


mu = n*p
var = n*p*(1-p)

#pnorm(1.96,0,1)
#  qnorm(0.975,0,1)
1-pnorm(9.5,mu ,sqrt(var))
1-(pnorm(9.5,mu ,sqrt(var))-pnorm(0,mu ,sqrt(var)))

#10<x<20
z1 = (10-1/2-mu)/(sqrt(var/n))
z2 = (20+1/2-mu)/(sqrt(var/n))

pnorm(20.5,mu,sqrt(var))-pnorm(9.5,mu ,sqrt(var))
pnorm(20,mu,sqrt(var))-pnorm(9.5,mu ,sqrt(var))

```
## approximately poisson
```{r}
lambda = n*p
1 - ppois(9,lambda)
```
Both the approximately normal and poisoson distributions are not appropriate distribution of the binominal one in the specific senarios, because both of them do not satisfy the critiria of transmission, which is ... 

# Problem 4
## a)

paired-t.test
```{r}
with(sleep,
     t.test(extra[group == 2],
            extra[group == 1], paired = TRUE,
            alternative = "greater"))

with(sleep,sum((extra[group == 2]-extra[group == 1])))
with(sleep,sqrt(sum((extra[group == 2]-extra[group == 1]-1.58)^2)/9))
with(sleep,sd(extra[group == 2]-extra[group == 1]))
1.58/(1.23/sqrt(10))
qt(0.95,9)
qnorm(0.95)
pnorm(1.64)
1-pt(4.0621,9)
1.58-1.83*1.23/sqrt(10)
```

## b) confidence interval

95% confidence

 0.7001142 2.4598858


## c) posteriori power

```{r}
delta=1.58
n=10
sd=
  with(sleep,
  sd(extra[group == 2]-extra[group == 1]))

power=
  pnorm(-qt(1-0.05,9)+delta/(sd/sqrt(n)))
power

```

## d) post hoc test

